%-------------------------
% Resume in Latex
% Author : Khairil Rahman Hakiki
% Based off of: https://github.com/kyyril/personal-web
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.1pt}

\urlstyle{same}

\raggedbottom
\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \textbf{#1} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4}
  \vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \small#1 \hfill \textit{\small #2}
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \small#1 \hfill #2
    \vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Khairil Rahman Hakiki} \\ \vspace{1pt}
    \small North Sumatera, Indonesia $|$ +6282274360915 $|$ \href{mailto:khairil.4hrp@gmail.com}{\underline{khairil.4hrp@gmail.com}} \\ \vspace{2pt}
    \href{https://linkedin.com/in/khairilrahman}{\underline{linkedin.com/in/khairilrahman}} $|$
    \href{https://github.com/kyyril}{\underline{github.com/kyyril}} $|$
    \href{https://kyyril.vercel.app}{\underline{kyyril.vercel.app}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {State Islamic University of Imam Bonjol Padang}{Padang, Indonesia}
      {Bachelor of Information Systems}{Aug. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Software Engineering, Statistics, Operating System, Network, Security, Project Management, Technopreneurship, Databases, and UI/UX Design.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Go (Golang)} \\
     \textbf{Frontend}{: React.js, Next.js, Vite, Redux Toolkit, Zustand, TanStack Query, Tailwind CSS, Shadcn UI} \\
     \textbf{Backend}{: Node.js, Express.js, GoFiber, RESTful APIs, Microservices, RabbitMQ, OAuth2.0, JWT} \\
     \textbf{Database \& ORM}{: PostgreSQL, Redis, MySQL, Prisma, TypeORM, GORM, Firebase, Supabase} \\
     \textbf{DevOps \& Tools}{: Docker, Kubernetes, Prometheus, Grafana, NGINX, GitHub Actions, Figma, Postman}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Sep. 2025 -- Des. 2025}
      {TIME Language Centre}{Padang, Indonesia}
      \resumeItemListStart
        \resumeItem{Spearheaded the modernization of legacy systems into a scalable \textbf{Microservices} architecture using \textbf{Go (Fiber)} and \textbf{Node.js}, significantly improving system maintainability and fault tolerance.}
        \resumeItem{Implemented \textbf{Domain-Driven Design (DDD)} principles to align software architecture with complex business logic, ensuring a robust and evolvable codebase.}
        \resumeItem{Optimized backend performance by integrating \textbf{Redis} for rate limiting, caching hot data and \textbf{RabbitMQ} for asynchronous event-driven processing, reducing API latency by 40\%.}
        \resumeItem{Orchestrated containerized deployments using \textbf{Docker} and \textbf{Kubernetes}, configuring \textbf{Horizontal Pod Autoscaling (HPA)} to handle high-traffic spikes seamlessly.}
        \resumeItem{Secured payment workflows by integrating \textbf{Xendit} payment gateway and enforced rigorous security standards with \textbf{OAuth 2.0} and \textbf{JWT} authentication.}
        \resumeItem{Ensured system structure and reliability by implementing comprehensive unit and integration testing using \textbf{Go-Test} and \textbf{Jest}, while establishing real-time monitoring and observability with \textbf{Prometheus} and \textbf{Grafana}.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Frontend Developer}{Apr. 2025 -- Des. 2025}
      {CodeAtHome}{Lampung, Indonesia}
      \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to build and maintain responsive web applications using \textbf{React.js} and \textbf{Next.js}, strictly adhering to clean code practices.}
        \resumeItem{Standardized frontend development workflows by implementing reusable component libraries with \textbf{Tailwind CSS} and \textbf{Shadcn UI}, accelerating feature delivery time.}
        \resumeItem{Enhanced application performance and state management efficiency using \textbf{TanStack Query} and \textbf{Redux}, resulting in a smoother user experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jan. 2025 -- Mar. 2025}
      {PT Astra International Tbk - TSO Auto2000}{Labuhanbatu, Rantauprapat}
      \resumeItemListStart
        \resumeItem{Engineered an AI-powered Car Recommendation System utilizing \textbf{Next.js} and \textbf{Generative AI}, streamlining the customer decision-making process and improving sales efficiency.}
        \resumeItem{Solved large-scale data quality issues by building an automated \textbf{Python} script to clean, transform, and standardize thousands of raw records into structured, analysis-ready datasets across multiple years (2010--2024).}
        \resumeItem{Developed 'ReminderApp', a critical internal tool for managing vehicle document renewals (STNK/BPKB), featuring role-based access control (RBAC) and automated notifications.}
        \resumeItem{Automated repetitive administrative tasks using \textbf{Google Apps Script}, reducing manual data entry workload by approximately 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://kyyril.vercel.app}{\underline{\textbf{Personal Website}}} $|$ \emph{Modern Fullstack Portfolio}}{}
          \resumeItemListStart
            \resumeItem{Engineered a high-performance personal platform using \textbf{Next.js}, featuring a custom \textbf{MDX}-based blog engine.}
            \resumeItem{Developed a low-latency interactive \textbf{Guestbook} service using \textbf{Bun} and \textbf{Elysia}, optimizing for rapid request handling.}
            \resumeItem{Integrated \textbf{Generative AI} to provide a context-aware conversational assistant for portfolio exploration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/kyyril/slither}{\underline{\textbf{Neon Slither}}} $|$ \emph{Real-Time Multiplayer Game}}{}
          \resumeItemListStart
            \resumeItem{Architected a high-performance multiplayer snake game using \textbf{Go}, \textbf{Redis}, and \textbf{WebSocket}, implementing \textbf{delta state compression} for \textbf{>95\% bandwidth reduction} in real-time sync.}
            \resumeItem{Engineered \textbf{client-side prediction} and \textbf{spatial hash grid} collision detection (O(n) vs O(n²)), enabling 10,000+ entities and smooth 60 FPS gameplay at 200ms+ latency.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://syncblog.vercel.app}{\underline{\textbf{SyncBlog}}} $|$ \emph{Full Stack Blog Platform}}{}
          \resumeItemListStart
            \resumeItem{Designed a scalable blogging architecture with a \textbf{Next.js} frontend and \textbf{Express.js} backend, ensuring clean separation of concerns.}
            \resumeItem{Implemented secure \textbf{OAuth} \& \textbf{JWT} authentication flows and real-time social features like comments and follows.}
            \resumeItem{Optimized frontend performance with \textbf{TanStack Query} for efficient data caching and \textbf{Redux} for complex state management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://hadith-api-go.vercel.app}{\underline{\textbf{Hadith API}}} $|$ \emph{High-Performance REST API}}{}
          \resumeItemListStart
            \resumeItem{Developed a high-throughput REST API in \textbf{Go (Gin)} tailored for querying massive religious datasets with sub-millisecond latency.}
            \resumeItem{Implemented optimized indexing strategies and efficient search algorithms to handle complex multi-parameter queries.}
            \resumeItem{Authored comprehensive \textbf{OpenAPI/Swagger} documentation to ensure seamless third-party developer integration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://saas-noteapp.vercel.app}{\underline{\textbf{SaaS NoteApp}}} $|$ \emph{Subscription Management System}}{}
          \resumeItemListStart
            \resumeItem{Built a secure, multi-tenant SaaS application integrating \textbf{Stripe} for sophisticated subscription billing lifecycles.}
            \resumeItem{Secured user sessions with \textbf{Kinde Auth} and enforced strict data isolation policies using \textbf{Supabase} RLS.}
            \resumeItem{Utilized \textbf{Prisma} with \textbf{PostgreSQL} for reliable data modeling and management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://designtocode-kohl.vercel.app}{\underline{\textbf{Design To Code}}} $|$ \emph{AI-Powered Frontend Generator}}{}
          \resumeItemListStart
            \resumeItem{Architected an AI-driven development tool leveraging \textbf{Generative AI} to transform UI mockups into production-ready \textbf{React} code.}
            \resumeItem{Built a scalable processing pipeline with \textbf{Next.js} and \textbf{Shadcn UI}, enabling customizable model selection.}
            \resumeItem{Implemented robust state management and persistence using \textbf{PostgreSQL}, \textbf{Prisma}, and \textbf{Cloudinary} for asset storage.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd




%-----------CERTIFICATIONS-----------
\section{Certifications}
 \resumeItemListStart
    \resumeItem{\href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=D4510B21F99D88A292FA173EA64DC122B01639350FCE422119EE1C499D08318E}{\underline{Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate}} -- Oracle}
    \resumeItem{\href{https://www.hackerrank.com/certificates/a8ba56e04468}{\underline{Frontend Developer (React)}} -- HackerRank}
    \resumeItem{\href{https://www.hackerrank.com/certificates/d1bbfc8bc93f}{\underline{REST API (Intermediate)}} -- HackerRank}
    \resumeItem{\href{https://www.hackerrank.com/certificates/9a23cd33889e}{\underline{Go (Basic)}} -- HackerRank}
    \resumeItem{\href{https://www.hackerrank.com/certificates/30deff9c5653}{\underline{JavaScript (Intermediate)}} -- HackerRank}
    \resumeItem{\href{https://freecodecamp.org/certification/khairilrahmanhakiki/responsive-web-design}{\underline{Responsive Web Design}} -- freeCodeCamp}
 \resumeItemListEnd


%-------------------------------------------
\end{document}
