%-------------------------
% Custom Cover Letter in Latex
% Author : Khairil Rahman Hakiki
%------------------------

\documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}

% Font options
% \usepackage[sfdefault]{roboto} 

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Khairil Rahman Hakiki} \\ \vspace{2pt}
    \small West Sumatra, Indonesia $|$ +6282274360915 $|$ \href{mailto:khairil.4hrp@gmail.com}{\underline{khairil.4hrp@gmail.com}} \\ \vspace{1pt}
    \href{https://linkedin.com/in/khairilrahman}{\underline{linkedin.com/in/khairilrahman}} $|$
    \href{https://github.com/kyyril}{\underline{github.com/kyyril}} $|$
    \href{https://kyyril.vercel.app}{\underline{kyyril.vercel.app}}
\end{center}

\vspace{0.5cm}

\today

\vspace{0.5cm}

\textbf{HENNGE Recruitment Team} \\
HENNGE K.K. \\
Shibuya, Tokyo \\
Japan

\vspace{0.8cm}

\textbf{Subject: Application for Global Internship Program (GIP) - Full Stack Engineering Pathway}

\vspace{0.5cm}

Dear HENNGE Recruitment Team,

I recently read the article from your engineering team about what makes a good candidate. I really liked that HENNGE looks for the ``Why'' behind the code, not just the skills. I also connect with the idea of ``Henka'' (Change) and being a ``Learnaholic.''

I am writing to apply for the \textbf{Global Internship Program (GIP)}. I believe my experience in building scalable systems fits well with what you are looking for.

My biggest learning moment was during my final thesis project with \textbf{TIME Language Centre}. They needed a system that could scale with their growing operations. Building this from scratch was a massive challenge. I decided to architect a \textbf{Microservices} solution because I wanted flexibility and long-term stability. This required me to learn entirely new concepts rapidly. This experience pushed me to be a true ``Learnaholic'', adapting to complex engineering challenges to solve real business problems.

Why HENNGE and why Japan? During my internship at \textbf{Toyota (Auto2000) in Indonesia}, I was introduced to the philosophy of \textit{Kaizen} (continuous improvement). I admired how this mindset was applied daily to refine processes. I see HENNGE as the embodiment of this spirit in the software world. I have a genuine passion for Japan and its culture, and I am driven to build my life and career in Tokyo, contributing to a team that values precision, innovation, and excellence.

I have finished my classes and am now just working on my thesis (graduating Nov 2026). I am available to join your internship immediately. I am excited to bring my skills in \textbf{Go} and \textbf{Microservices} to learn and grow with your team.

Thank you for reading my story.

\vspace{0.5cm}

Sincerely,

\vspace{0.2cm}

\textbf{Khairil Rahman Hakiki}

\end{document}
